### 2019-06-25 README.Rmd
updated talking points

- adding a random noise variable to the model to see if LIME ever chooses it as an important variable
- is it okay if I change the repo name to "lime-research"?
- can I remove some of the sources from the references file that I am not going to use?
- I finished writing and editing the introduction - what do you think?

>>>>

- adding a random noise variable to the model to see if LIME ever chooses it as an important variable
- can I remove some of the sources from the references file that I am not going to use?
